\documentclass[12pt,a4paper,sans]{moderncv}
\moderncvtheme[blue]{classic}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\recomputelengths
\nopagenumbers{}

% personal data
\firstname{Shaun}
\familyname{Taheri}
\title{Distributed Systems Engineer}
%\address{}{}
%\mobile{}
%\phone{}
%\fax{}
\email{cv@taheris.net}
%\homepage{}
\social[github]{taheris}
\social[linkedin]{taheris}
%\extrainfo{}
%\photo[64pt][0.4pt]{picture}
%\quote{}

\begin{document}
\makecvtitle


\vspace{-0.5em}
\section{Skills}

\vspace{0.5em}
\cvitem{Architecture}{
  Leading large-scale distributed systems projects from conception to delivery.
}

\vspace{0.5em}
\cvitem{Language}{
  Production experience across a range of languages and paradigms, specializing in building high-performance backends in Rust.
}

\vspace{0.5em}
\cvitem{Infrastructure}{
  Extensive operational experience with high-volume message brokers plus a range of relational, non-relational and distributed databases.
}

\section{Experience}

\vspace{0.5em}
\cventry{Jan 2019 -- Dec 2022}{Lead Backend Engineer}{\httpslink[Kraken Digital Asset Exchange]{www.kraken.com}}{Remote}{}{
  \begin{itemize}
  \setlength\itemsep{0.5em}
  \vspace{-0.5em}
  \item
    Ported the existing backend from PHP to Rust, while adding new features and defining the standards for new Rust services.
  \item
    Design and implementation of a risk-engine to score streams of real-time events, identifying potential account takeovers and preventing fraudulent transactions.
  \item
    Led the core backend transition to an event-driven architecture, replacing RPC calls between services while supporting backwards and forwards compatible changes.
  \end{itemize}
  \vspace{0.5em}
}

\cvline{\footnotesize\textit{keywords}}{\footnotesize\textit{crypto, rust, event-driven architecture, team lead, kafka, nomad, protobuf}}
\vspace{0.5em}

\vspace{0.5em}
\cventry{Mar 2016 -- Dec 2018}{Senior Developer}{\httpslink[Advanced Telematic Systems]{www.here.com/learn/blog/here-will-acquire-advanced-telematic-systems-to-power-ultra-secure-data-transmissions}}{Berlin}{}
{
  \begin{itemize}
  \setlength\itemsep{0.5em}
  \vspace{-0.5em}
  \item
    Built an open-source Rust client for securely applying Software-Over-The-Air updates targeting embedded Linux devices within automotive fleets.
  \item
    Wrote an implementation for broadcasting atomic updates to microcontrollers within cars. Presented a demo to HERE Technologies who subsequently acquired the company.
  \item
    Introduced Infrastructure as Code utilizing Nix for deterministic deployments within cloud and data-center environments.
  \end{itemize}
  \vspace{0.5em}
}

\cvline{\footnotesize\textit{keywords}}{\footnotesize\textit{automotive, rust, cryptography, nix, kubernetes, sota, yocto, embedded linux}}
\vspace{0.5em}

\vspace{0.5em}
\cventry{Nov 2014 -- Feb 2016}{Senior Developer}{\httpslink[Optiopay]{www.optiopay.com}}{Berlin}{}
{
  \begin{itemize}
  \setlength\itemsep{0.5em}
  \vspace{-0.5em}
  \item
    Design and implementation of a microservice architecture where Event Sourcing was used to build fault-tolerant Go services that could scale to varying workloads.
  \item
    Built the continuous delivery pipeline for containerized services across CoreOS machines using a distributed key-value store for service discovery.
  \end{itemize}
  \vspace{0.5em}
}

\cvline{\footnotesize\textit{keywords}}{\footnotesize\textit{fintech, go, kafka, microservices, event-sourcing, continuous delivery, coreos, etcd}}
\vspace{0.5em}

\vspace{0.5em}
\cventry{Oct 2013 -- Sep 2014}{Senior Developer}{\httpslink[LShift]{www.oliverwyman.com/media-center/2016/oliver-wyman-acquires-the-business-of-the-independent-software-d.html}}{London}{}
{
  \begin{itemize}
  \setlength\itemsep{0.5em}
  \vspace{-0.5em}
  \item
    Development of a typesetting platform to extract content and structure from documents in Google Docs and output template-formatted PDFs for academic publishing.
  \item
    Provided consultation on how to manage a heterogeneous set of relational databases across a range of clients. The recipient subsequently acquired the company.
  \item
    Built an internal document indexer in Go using ElasticSearch for rapid searching over a large corpus.
  \end{itemize}
  \vspace{0.5em}
}

\cvline{\footnotesize\textit{keywords}}{\footnotesize\textit{consulting, java, python, ruby, go, julia, elasticsearch}}
\vspace{0.5em}

\vspace{0.5em}
\cventry{Mar 2008 -- Sep 2012}{Data Analyst $\rightarrow$ Senior Data Analyst}{\httpslink[Centrica]{www.centrica.com}}{Edinburgh}{}
{
  \begin{itemize}
  \setlength\itemsep{0.5em}
  \vspace{-0.5em}
  \item
    Analysis of terabyte-scale datasets using SAS to automate billing processes, with an improvement over the previous system from £4m to £7m per annum.
  \item
    Built an internal portal for self-service analytics, reducing complex report turnaround time for senior management from days to minutes.
  \item
    Manager for a team of data analysts. At the time I was the youngest person to be promoted to a senior position within the office.
  \end{itemize}
  \vspace{0.5em}
}

\cvline{\footnotesize\textit{keywords}}{\footnotesize\textit{energy, sas, proc sql, vba, python, javascript, analytics, management}}
\vspace{0.5em}


\section{Education}

\vspace{0.5em}
\cventry{Sep 2012 -- Aug 2013}{MSc Computer Science}{}{University College London}{}
{
  \begin{itemize}
  \setlength\itemsep{0.5em}
  \vspace{-0.5em}
  \item
    Electives in functional programming and information retrieval.
  \item
    One of the top performers with an exam average over 85\%.
  \end{itemize}
  \vspace{0.5em}
}

\vspace{0.5em}
\cventry{Sep 2005 -- May 2009}{MA Economics}{}{University of Edinburgh}{}
{
  \begin{itemize}
  \setlength\itemsep{0.5em}
  \vspace{-0.5em}
  \item
    Electives in game theory and econometrics.
  \item
    Final year dissertation on approximating optimal play in Texas Hold\textsc{\char13}em poker.
  \end{itemize}
  \vspace{0.5em}
}

\end{document}
